---
title: "Primary Care Homeless Health Data"
output: 
  html_document:
    theme: sandstone
    highlight: tango
    ##toc: true
    ##toc_float: true
runtime: shiny
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(plyr)
library(dplyr)


```

*This business of people just dying like animals, for instance, with nobody standing by, nobody interested, the death not even noticed till the morning* ~  George Orwell _from_ How The Poor Die
 

## {.tabset  .tabset-fade .tabset-pills}

### Background

This site is a collaboration between clinician and computer scientist to help bridge the gap in the paucity of homeless health data.  Please click on the tabs above to create your own graphs where mortality and population level data can be viewed.

Over time we hope that all homeless primary care services will be happy to share their anonymized data on this site, we hope that the contributing services will find the data we show to be of use, at the very least we hope to be able to provide a picture of what the health of homeless is like. We dare to dream further however, and hope that this site in time may allow us to know where to focus our efforts and play a part, however small in improving the health care outcomes of our homeless patients.

Whilst the greatest care has been taken in extrapolating the data, front line clinicians know that the medical record can only tell you so much. Electronic system are hard task masters when it comes to coding data and it would be fair assumptions that most of the epidemiology presented is an underestimate of the actual figure. 

We hope the data on this site will be of use. We welcome any feedback, requests for collaboration or criticisms. 
Add some background info

### Causes of Death

Using the fields below select the data you would like to use to draw up a bar plot of looking at the cause of homeless death. *On the x axis we would have cause of death and the y axis age of death.*

```{r causes_of-death, echo=FALSE}

Death <- read.csv("Data/Death.csv", header=TRUE, sep=",", as.is=TRUE)

inputPanel(
  selectInput("age_at_death", label = "Age at death:",
              choices = c("All ages", "Under 30", "30-40", "40-50", "50-60", "Over 60"), selected = "All ages"),
  
  selectInput("practice", label = "Which Practice:",
              choices = c("All", "Health E1", "The Greenhouse"), selected = "All"),

  selectInput("place_of_death", label = "Place of Death:",
              choices = c("Anywhere", "Hospital", "Hospice", "Street", "Home"), selected = "Anywhere"),  
  
   selectInput("gender", label = "Gender:",
              choices = c("All", "Male", "Female"), selected = "All"),

  checkboxInput("htn", label= "Hypertension", value = FALSE, width = NULL),
  checkboxInput("diabetes", label= "Diabetes", value = FALSE, width = NULL),
  checkboxInput("antipsychotic", label= "On Anti-psychotic", value = FALSE, width = NULL),
  checkboxInput("hepB", label= "Hepatitis B", value = FALSE, width = NULL),
  checkboxInput("hepC", label= "Hepatitis C", value = FALSE, width = NULL),
 
  sliderInput("alcohol", label = "Units of alcohol drunk are less than:",
              min = 0, max = 600, value = 20, step = 10)
)

renderPlot({
  ##barplot(xtabs(~Death$Classification_of_Death), las=2)
  
  
      age_at_death <- c(input$age_at_death)
      if(input$age_at_death == "Under 30")
      {
        Death <- Death %>%
            filter(Age_at_Death < 30)
      }
      else if(input$age_at_death == "30-40")
      {
        Death <- Death %>%
            filter(Age_at_Death>30)
        
        Death <- Death %>%
            filter(Age_at_Death<40)
      }
      else if(input$age_at_death == "40-50")
      {
        Death <- Death %>%
            filter(Age_at_Death>40)
        
        Death <- Death %>%
            filter(Age_at_Death<50)
      }
      else if(input$age_at_death == "40-50")
      {
        Death <- Death %>%
            filter(Age_at_Death>40)
        
        Death <- Death %>%
            filter(Age_at_Death<50)
      }
      else if(input$age_at_death == "50-60")
      {
        Death <- Death %>%
            filter(Age_at_Death>50)
        
        Death <- Death %>%
            filter(Age_at_Death<60)
      }
      else if(input$age_at_death == "Over 60")
      {
        Death <- Death %>%
            filter(Age_at_Death>60)
      }
    
      
      practice <- c(input$practice)
      if(input$practice != "All")
      {
      Death <- Death %>%
           filter(Practice %in% input$practice)
      }
      
      place_of_death <-c(input$place_of_death)
      if(input$place_of_death != "Anywhere")
      {
        Death <- Death %>%
          filter(Place_of_Death %in% input$place_of_death)
      }
      
      gender <-c(input$gender)
      if(input$gender != "All")
      {
        Death <- Death %>%
          filter(Gender %in% input$gender)
      }
      
      htn <-c(input$htn)
      if(input$htn)
      {
        Death <- Death %>%
            filter(HTN %in% input$htn)
      }
      
      antipsychotic <-c(input$antipsychotic)
      if(input$antipsychotic)
      {
        Death <- Death %>%
            filter(On_Antipsychotic %in% input$antipsychotic)
      }
      
      hepB <-c(input$hepB)
      if(input$hepB)
      {
        Death <- Death %>%
            filter(HepB %in% input$hepB)
      }
      
      hepC <-c(input$hepC)
      if(input$hepC)
      {
        Death <- Death %>%
            filter(HepC %in% input$hepC)
      }

      Death <- Death %>%
            filter(Alcohol > input$alcohol)
  
      b <- ggplot(Death, aes(x=Classification_of_Death)) +
       geom_bar(stat="count", width=0.7, fill="steelblue")  
      print(b)
  
})

##pie(table(x))

```

### Plot Associations

Here it would be nice if we had some scatter plots. 


```{r associations, echo=FALSE}

Death <- read.csv("Data/Death.csv", header=TRUE, sep=",", as.is=TRUE)

inputPanel(
  selectInput("yaxis", "Y axis Value:",
                list("Units of Alcohol" = "Alcohol",
                     "Last Systolic Blood Pressure" = "Last_Systolic"))
)


renderText({ 
      a= "Death$"
      paste0(a,input$yaxis)
    })


renderPlot({
  
      
      if(input$yaxis == "Alcohol"){

      p <- ggplot(Death, aes(x=Age_at_Death, y=Alcohol), fill=Practice) +
      geom_point(shape=1, size=3, na.rm=TRUE, aes(color=Practice, shape=Practice))
      print(p)
      
      }
      
  if(input$yaxis == "Last_Systolic"){
  
      p <- ggplot(Death, aes(x=Age_at_Death, y=Last_Systolic)) +
      geom_point(shape=1, size=5)
      print(p)
  }
})

```

### Practice Level Epidemiology

Please select from the fields below the epidemiological data submitted by practices. Would be good to let practices compare by regions and against indiviudal practices.

I think to keep the graph uncluttered we would have to have a check box to display the type of data that wants to be viewed e.g. hepatitis prevalance. May just have a drop down menu saying All/Male/Female.

May be a useful feature to compare the trends in one practice over time also.


### Trends Over Time

Here I thought we could allow death data to be viewed over a time. Maybe by drop down box allowing people to choose the year or cause of death....but I wonder if there is a more elegant soloution?

### Access Raw Data

Add some tables and discussion here. Is it easy to run reports. For example could someone slect - show me where cause of death is "Decompensated Liver Disease"?

```{r echo=FALSE}
renderDataTable({iris})
```

### Links

[Crisis Report Into Homless Death](http://www.crisis.org.uk/data/files/publications/Homelessness%20kills%20-%20Executive%20Summary.pdf).

### About
