---
title: "Primary Care Homeless Mortality Data"
output: 
  html_document:
    theme: sandstone
    highlight: tango
runtime: shiny
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(plyr)
library(dplyr)

```

*"This business of people just dying like animals, for instance, with nobody standing by, nobody interested, the death not even noticed till the morning"* ~  George Orwell writing in "_How The Poor Die_"
 

## {.tabset  .tabset-fade .tabset-pills}

### Background

This site is a repostary of homeless mortality data from within the primary care services. Please use the tabs above to view and manipulate the data.

Over time we hope that all health services dealing with the health of the homeless will be happy to share their anonymized data on this site. We hope that clinicians and researchers may find the data to be of use and, at the very least we hope to be able to provide a picture of what the health of homeless is like. We dare to dream further however, and hope that this site in time may allow us to know where to focus our efforts and play a part, however small, in improving the health care outcomes of our homeless patients.

Whilst the greatest care has been taken in extrapolating the data, front line clinicians know that the medical record can only tell you so much. Electronic system are hard task masters when it comes to coding data and it would be fair assumptions that most of the epidemiology presented is an underestimate of the actual figure.

We hope the data on this site will be of use. We welcome any feedback, requests for collaboration or criticisms. 

### Causes of Death

Using the fields below select the data you would like to use to draw up a bar plot of looking at the cause of homeless death. 

```{r causes_of-death, echo=FALSE}

death_data = read.csv("../homeless_data/Death.csv", header=TRUE, sep=",", as.is=TRUE, stringsAsFactors=FALSE)
colnames(death_data) = tolower(colnames(death_data))

inputPanel(
  selectInput("age_at_death", label = "Age at death:",
              choices = c("All ages", "Under 30", "30-40", "40-50", "50-60", "Over 60"), selected = "All ages"),
  
  selectInput("practice", label = "Which Practice:",
              choices = c("All", "Health E1", "The Greenhouse"), selected = "All"),

  selectInput("place_of_death", label = "Place of Death:",
              choices = c("Anywhere", "Hospital", "Hospice", "Street", "Home"), selected = "Anywhere"),  
  
   selectInput("gender", label = "Gender:",
              choices = c("All", "Male", "Female"), selected = "All"),

  checkboxInput("htn", label= "Hypertension", value = FALSE, width = NULL),
  checkboxInput("dm", label= "Diabetes", value = FALSE, width = NULL),
  checkboxInput("antipsychotic", label= "On Anti-psychotic", value = FALSE, width = NULL),
  checkboxInput("hepB", label= "Hepatitis B", value = FALSE, width = NULL),
  checkboxInput("hepC", label= "Hepatitis C", value = FALSE, width = NULL),
 
  sliderInput("alcohol", label = "Units of alcohol consumed are more than or equal to:",
              min = 0, max = 600, value = 20, step = 10)
)

renderPlot({
      if(input$age_at_death == "Under 30"){
        death_data = death_data %>%
            filter(age_at_death < 30)
      } else if(input$age_at_death == "30-40"){
        death_data = death_data %>%
            filter(age_at_death>30 & age_at_death<40)
      } else if(input$age_at_death == "40-50"){
        death_data = death_data %>%
            filter(age_at_aeath>40 & age_at_aeath<50)
      } else if(input$age_at_death == "40-50"){
        death_data = death_data %>%
            filter(age_at_death>40 & age_at_aeath<50)
      } else if(input$age_at_death == "50-60"){
        death_data = death_data %>%
            filter(age_at_death>50 & age_at_death<60)
      } else if(input$age_at_death == "Over 60"){
        death_data = death_data %>%
            filter(age_at_aeath>60)
      }
    
      if(input$practice != "All"){
        death_data = death_data %>%
           filter(practice %in% input$practice)
      }
      
      if(input$place_of_death != "Anywhere"){
        death_data = death_data %>%
          filter(place_of_death %in% input$place_of_death)
      }
      
      if(input$gender != "All"){
        death_data = death_data %>%
          filter(gender %in% input$gender)
      }
      
      if(input$htn){
        death_data = death_data %>%
            filter(htn %in% input$htn)
      }
      
      if(input$dm){
        death_data = death_data %>%
            filter(diabetes %in% input$dm)
      }
  
      if(input$antipsychotic){
        death_data = death_data %>%
            filter(on_antipsychotic %in% input$antipsychotic)
      }
      
      if(input$hepB){
        death_data = death_data %>%
            filter(hepb %in% input$hepB)
      }
      
      if(input$hepC){
        death_data = death_data %>%
            filter(hepc %in% input$hepC)
      }

      death_data = death_data %>%
            filter(alcohol >= input$alcohol)
  
      b = ggplot(death_data, aes(x= classification_of_death)) +
           xlab("Classification of Death") +
           ylab("Count") +
           geom_bar(stat="count", width=0.7, fill="steelblue")+
           theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
      print(b)
  
})

```

### Plot Associations

Please use the drop down menu below to decide on what the y-axis should be. The x-axis is a static field and indicates cause of death. 


```{r associations, echo=FALSE}

death_data = read.csv("../homeless_data/Death.csv", header=TRUE, sep=",", as.is=TRUE, stringsAsFactors=FALSE)
colnames(death_data) = tolower(colnames(death_data))

inputPanel(
  selectInput("yaxis", "Y axis Value:",
                list("Units of Alcohol" = "alcohol",
                     "Last Systolic Blood Pressure" = "last_systolic",
                     "Last Diastolic Blood Pressure" = "last_diastolic",
                     "Days Since Last Seen" = "time_since_seen"))
)

renderPlot({
        q = ggplot(death_data, aes_string(x="age_at_death", y=input$yaxis)) +
               geom_point(shape=1, size=3, na.rm=TRUE, aes(color=practice, shape=practice)) + 
               xlab("Age at Death") + 
               ylab(gsub("_"," ",input$yaxis))
        print(q)
})

```

### Practice Level Epidemiology

Please select from the fields below the epidemiological data submitted by practices.


```{r population, echo=FALSE}

population_data = read.csv("../homeless_data/Population.csv", header=TRUE, sep=",", as.is=TRUE, stringsAsFactors=FALSE)
colnames(population_data) = tolower(colnames(population_data))


inputPanel(
  selectInput("cond", label = "Condition for comparison:",
              choices = list("Harmful Alcohol Abuse" = "alcohol",
                             "Opiod Addiction" = "opiod",
                             "Bendzodiazapine Misuse" = "bendzo",
                             "Viral Hepatitis" = "hep",
                             "HIV" = "hiv",
                             "Diabetes" = "dm",
                             "Hypertension" = "htn",
                             "On Anti-Psychotic" = "antipsych",
                             "Sex Workers" = "sw",
                             "Victim of Domestic Violence or Rape" = "dv"), 
              selected = "alcohol"),

   selectInput("sex", label = "Gender:",
              choices = c("All", "Male", "Female"), selected = "All")  
)


renderPlot({
          yax = paste0(input$cond,"_",input$sex)
          t = ggplot(population_data, aes_string("place", tolower(yax))) +
               geom_bar(stat="identity")
          print(t)
})

```


### Trends Over Time

This part of the site is still under construction. In time we hope that it will present a practice specific time series. 

```{r time, echo=FALSE}


```

### Access Summary Tables

Tables of key descriptive statistics will appear here to give the user an understanding of the underlying data without being disclosive of sensitive data.

```{r echo=FALSE}
# I don't think showing this data publically is a smart idea so commented out
# perhaps just put aggregates here
#renderDataTable({Death})
```

